Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-07-10 WholePlotTrajectories.Rmd
coquille

```{r NMDSplans, out.width = '100%', echo=FALSE, fig.cap="Plot trajectories in terms of flora composition (left panels (ref:Bolda) and (ref:Boldc)) and functional composition (right panels (ref:Boldb) and (ref:Boldd)) in a two-dimensional NMDS space. Lower panels ((ref:Boldc) and (ref:Boldd)) represent the euclidean distance to initial condition along the 30 sampled years. Colors are treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals", fig.env="figure*"}
load("DB/FunctionalComposition_forGraphs");load("DB/TaxoComposition_forGraphs")
load("DB/FunDistance_ForGraphs");load("DB/TaxoDistance_ForGraphs")

@@

```{r CWM, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the communities weighted means (CWM) over 30 years after disturbance of 4 leaf traits (Leaf thickness, (ref:capThickness), chlorophyll content, (ref:capChloro), toughness, (ref:capThoughness) and specific area, (ref:capSLA)), 2 stem traits (wood specific gravity, (ref:capWSG), and bark thickness, (ref:capBarkThick)) and one life history trait (Specific maximum height at adult stage, (ref:capHmax)). Colors are treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure*"}
load("DB/CWM")

@@

```{r DivTaxo, out.width = '100%', echo=FALSE, fig.cap="Trajectories over 30 years of the difference with the 1989 inventory (2 years after disturbance) of community taxonomic (ref:Bolda) richness, (ref:Boldb), taxonomic evenness, (ref:Boldc) functional richness, and (ref:Boldd) functional evenness. Colors are treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals ", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")
load("DB/FunctionalTraj_ForGraphs")
load("DB/FunctionalRichnessTraj_ForGraphs")

@@

```{r IDHplot, out.width = '100%', echo=FALSE, fig.asp = 1.5/3,fig.cap="Relationship between the initial \\%AGB loss and community taxonmic richness (ref:Bolda), taxonomic evenness (ref:Boldb), functional richness (ref:Boldc),and functional evenness (ref:Boldd) at 10, 20 and 30 years after disturbance. Colors are treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals ", fig.env="figure*"}
load("DB/RichnessIDH");load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB");load("DB/FunRichIDH")

@@

```{r RedFun_rest, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), blue (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure"}
load("DB/Redundancy_restricted")

>>>>

```{r NMDSplans, out.width = '100%', echo=FALSE, fig.cap="Plot trajectories in terms of flora composition (left panels (ref:Bolda) and (ref:Boldc)) and functional composition (right panels (ref:Boldb) and (ref:Boldd)) in a two-dimensional NMDS space. Lower panels ((ref:Boldc) and (ref:Boldd)) represent the euclidean distance to initial condition along the 30 sampled years. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure*"}
load("DB/FunctionalComposition_forGraphs");load("DB/TaxoComposition_forGraphs")
load("DB/FunDistance_ForGraphs");load("DB/TaxoDistance_ForGraphs")

@@

```{r CWM, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the communities weighted means (CWM) over 30 years after disturbance of 4 leaf traits (Leaf thickness, (ref:capThickness), chlorophyll content, (ref:capChloro), toughness, (ref:capThoughness) and specific area, (ref:capSLA)), 2 stem traits (wood specific gravity, (ref:capWSG), and bark thickness, (ref:capBarkThick)) and one life history trait (Specific maximum height at adult stage, (ref:capHmax)). Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure*"}
load("DB/CWM")

@@

```{r DivTaxo, out.width = '100%', echo=FALSE, fig.cap="Trajectories over 30 years of the difference with the 1989 inventory (2 years after disturbance) of community taxonomic (ref:Bolda) richness, (ref:Boldb), taxonomic evenness, (ref:Boldc) functional richness, and (ref:Boldd) functional evenness. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals ", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")
load("DB/FunctionalTraj_ForGraphs")
load("DB/FunctionalRichnessTraj_ForGraphs")

@@

```{r IDHplot, out.width = '100%', echo=FALSE, fig.asp = 1.5/3,fig.cap="Relationship between the initial \\%AGB loss and community taxonmic richness (ref:Bolda), taxonomic evenness (ref:Boldb), functional richness (ref:Boldc),and functional evenness (ref:Boldd) at 10, 20 and 30 years after disturbance. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals ", fig.env="figure*"}
load("DB/RichnessIDH");load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB");load("DB/FunRichIDH")

@@

```{r RedFun_rest, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure"}
load("DB/Redundancy_restricted")
